Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-09-26 paper.qmd
Figure 13 removed long edge in PaCMAP
Figure 13, updated after removing long edges manually for UMAP
Updated Figure 13 tSNE layout by manually removing long edges

tr_from_to_df_gau1 <- tr_from_to_df_gau1 |>
  filter(row_number() != 149)

@@

distance_df_small_edges_gau1 <- distance_gau1 |>
  filter(distance < benchmark_gau1)

@@

distance_df_small_edges <- distance_df_small_edges |>
  filter(row_number() != 108)

@@

distance_df_small_edges_gau1 <- distance_gau1 |>
  filter(distance < benchmark_gau1)

@@

distance_df_small_edges_gau1 <- distance_gau1 |>
  filter(distance < benchmark_gau1)

>>>>

# tr_from_to_df_gau1 <- tr_from_to_df_gau1 |>
#   filter(row_number() != 149)

@@

distance_df_small_edges_gau1 <- distance_gau1 |>
  filter(distance < benchmark_gau1) |>
  filter(!(row_number() %in% c(33, 40, 48, 138, 143)))

@@

# distance_df_small_edges <- distance_df_small_edges |>
#   filter(row_number() != 108)

@@

distance_df_small_edges_gau1 <- distance_gau1 |>
  filter(distance < benchmark_gau1) |>
  mutate(ID = row_number()) |>
  filter(!(ID %in% c(112)))

@@

distance_df_small_edges_gau1 <- distance_gau1 |>
  filter(distance < benchmark_gau1) |>
  mutate(ID = row_number()) |>
  filter(!(ID %in% c(97)))
